%-------------------------------------------------------------------------------
%-------------------------------------------------------------------------------
\documentclass{brandeis-dissertation}
\usepackage{amsmath}
\usepackage{pdfpages}
\usepackage{setspace} 
\usepackage{float}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{graphicx}
\graphicspath {{figures/}}
\usepackage[utf8x]{inputenc}
\usepackage{subfig}
\usepackage{indentfirst}
% package for including graphics with figure-environment
\usepackage{hyperref}
% colored borders (false) colored text (true)
\hypersetup{colorlinks=true,citecolor=blue,filecolor=black,linkcolor=blue,urlcolor=blue}
\usepackage{natbib}
%\usepackage[style=phys]{biblatex} 
%\setupttoc{toc}{numbered}
\newcommand{\Ztt}{Z\rightarrow\tau\tau}
% Add you own definitions here (file ANA-HIGG-2018-49-INT1-defs.sty).
%\usepackage{ANA-HIGG-2018-49-INT1-defs}

%-------------------------------------------------------------------------------
% Generic document information
%-------------------------------------------------------------------------------

% Title, abstract and document 
\title{\normalsize{Measurement of the vector boson fusion production Higgs boson fiducial cross-section observed in the $WW^*\rightarrow\ell\nu\ell\nu$ decay channel with the ATLAS detector}}
\author{Laura Bergsten}
\department{Department of Physics}
\advisor{Professor Gabriella Sciolla, Department of Physics, Brandeis University}
\reader{Professor Craig Blocker, Department of Physics, Brandeis University}
\reader{Dr. Alessandro Tricoli, Brookhaven National Laboratory}
%\signoff{Eric Chasalow}{Dean}
\dean{Eric Chasalow}
\graduationmonth{August}
\graduationyear{2020}
%-------------------------------------------------------------------------------
% Content
%-------------------------------------------------------------------------------
\begin{document}
%\signaturepage*
\thesisabstract{Vector boson fusion produced Higgs boson fiducial and inclusive cross-sections are measured in the $H\rightarrow WW^*\rightarrow\ell\nu\ell\nu$ decay channel using 139 fb$^{-1}$ of proton-proton collisions. Collisions from the Large Hadron Collider at $\sqrt{s}=13$ TeV are recorded by the ATLAS detector. New analysis techniques are developed to accurately estimate contamination from top decays and gluon-gluon fusion production Higgs events. An excess of vector boson fusion Higg decays are observed over Standard Model backgrounds with a significance of 6.6$\sigma$, the most conclusive observation of this Higgs production mode in the $WW^*$ channel to date. The fiducial and inclusive cross-sections are measured to be 2.78$^{+0.56}_{-0.52}$~fb and $89.2^{+18.3}_{-17.3}$~fb, respectively. No significant deviations from Standard Model predictions are observed.}
%\dedication{}
\acknowledgments{This thesis, and the entirety of my Ph.D. journey, were possible because of support and assistance from many groups and individuals, only some of which I list here. 

First, thank you to my advisor \textbf{Prof. Gabriella Sciolla}. Over the past five years, you have helped me become a better teacher, researcher, and physicist. The many hours you spent helping me practice for oral qualifiers my first year, the long walks around Brookhaven where you dispensed science and life advice, and the innumerable coffee chats at CERN, BNL, and Brandeis all pushed me to grow, learn, and finally, to finish my Ph.D.  

Thank you also to \textbf{Prof. Craig Blocker} and \textbf{Dr. Alessandro Tricoli} for serving on my thesis committee. Your comments enabled me to think more deeply about the subject matter and become a better writer. I owe additional thanks to Alessandro for leading my analysis team. Our weekly meetings encouraged me to think about problems in new ways and your guidance is evidenced throughout this thesis.  

I am grateful to the VBF $H\rightarrow WW^* \rightarrow \ell\nu\ell\nu$ differential group, whose team-wide efforts contributed to the measurements I detail here. I would especially like to thank \textbf{Dr. Gaetano Barone} and \textbf{Sagar Addepalli}; Gaetano, for teaching me how to complete a physics analysis and providing help in everything from statistics to debugging and Sagar, for taking over many of my responsibilties in the analysis and for the thoughtful questions and contributions you made in the past months. 

Next I would like to thank all my Brandeis labmates, but in particular \textbf{Prajita Bhattarai} for always saying ``yes'' to an adventure, \textbf{Dr. Hannah Herde} for her constant support and encouragement, and \textbf{Jiayi Chen} for tea breaks and friendship. 

While it only features briefly in this thesis, my time at Brookhaven National Lab was a formative experience and I appreciate the entire ITk strips community for their welcome. I want to highlight \textbf{Dr. Dave Lynn} for leading my thermomechanical stave testing efforts and \textbf{Dr. Stefania Stucci} for her mentorship at BNL.

None of this work would have been possible without the love and support of my friends and family. To my parents, \textbf{Bob and Liz,} thank you for constantly reminding me of the world beyond particle physics and cheering every accomplishment, big or small. To my grandma, \textbf{Jackie,} for instilling the importance of education in me and being my (and Nicks'!) biggest fan. To my sisters, \textbf{Lissy and Sabrina,} for understanding all of my jokes and inspiring me with all youhave each accomplished. And finally, I need to thank \textbf{Nick.} We met while I was in the midst of my first year at Brandeis and in the time that followed you took endless trips on trains, ferries, and planes to visit each new place I called home. Your confidence in me is infectious and I am at my best in your company.  I can't wait to begin the next set of adventures beside you. 
}
\thesisfront[lot,lof] %other options include onlinesubmission, copyright, nocopyright, lot, nolot, lof, nolof
\clearpage
%\begin{doublespacing}
%\cleardoubleoddpage
%\pagenumbering{roman}
%sectionnumbering{roman}
%\listoftables
%\listoffigures
%\end{doublespacing}
%\tableofcontents

%-------------------------------------------------------------------------------
%-------------------------------------------------------------------------------
%\pagenumbering{arabic}
%\sectionnumbering{arabic}
\chapter{Introduction}
\label{sec:intro}
\input{sections/Introduction}
\clearpage
%-------------------------------------------------------------------------------
%-------------------------------------------------------------------------------
%-------------------------------------------------------------------------------
\chapter{Theory}
\label{sec:theory}
\input{sections/Theory}
\clearpage
%-------------------------------------------------------------------------------
%-------------------------------------------------------------------------------
%-------------------------------------------------------------------------------
\chapter{The LHC and the ATLAS detector}
\label{sec:LHCandATLAS}
\input{sections/LHCandATLAS}
\clearpage
%-------------------------------------------------------------------------------
%-------------------------------------------------------------------------------
%-------------------------------------------------------------------------------
\chapter{Reconstruction of Physics Objects}
\label{sec:TrackingIso}
\input{sections/TrackingIso}
\clearpage
%-------------------------------------------------------------------------------
%-------------------------------------------------------------------------------
%-------------------------------------------------------------------------------
\chapter{Event Selection}
\label{sec:EventSelection}
\input{sections/EventSelection}
\clearpage
%-------------------------------------------------------------------------------
%-------------------------------------------------------------------------------
%-------------------------------------------------------------------------------
\chapter{Backgrounds and Systematics}
\label{sec:BackgroundsSys}
\input{sections/BackgroundsSys}
\clearpage
%-------------------------------------------------------------------------------
%-------------------------------------------------------------------------------
%-------------------------------------------------------------------------------
\chapter{Results}
\label{sec:Results}
\input{sections/Results}
\clearpage
%-------------------------------------------------------------------------------
%-------------------------------------------------------------------------------
%-------------------------------------------------------------------------------
%\clearpage
%\chapter{FakeClosure}
%\input{sections/FakeClosre}

\clearpage
\chapter{Conclusions and Outlook}
\label{sec:conclusion}
\input{sections/Conclusion}
%-------------------------------------------------------------------------------

\clearpage
\begin{singlespacing}
\bibliographystyle{unsrt}
\bibliography{references}
\end{singlespacing}

%-------------------------------------------------------------------------------
\clearpage
\appendix
\chapter{Inner Tracker}
\label{sec:ITk}
\input{sections/InnerTracker}
\chapter{$Z+$jets BDT}
\label{sec:ZjetsBDT}
\input{sections/ZjetsBDT}
\chapter{Multi-dimensional BDT}
\label{sec:3DBDT}
\input{sections/3DBDT}
%-------------------------------------------------------------------------------
\clearpage
\end{document}
